%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large Samadhi समाधि}
\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Introduction}

Tadevartho-matra-nibhasing-swarupashunyamibo Samadhi

तदेवार्थमात्रनिर्भासं स्वरुपशून्यमिव समाधि||

	\begin{itemize}
	\item When that giving up all forms, 
reflects  only  the  meaning  it  is 
Samadhai. 
	\item That comes when in 
meditation  the  form  or  the 
external part is given up.
	\end{itemize}

\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Stages of Meditation/ Samadhi समाधी}


	\begin{itemize}
	\item Savitarka ( सवितर्क) :concentrate on gross objects
	\item  Nirvitarka (निर्वितर्क): go beyond gross objects
	\item  Savichara (सविचार): concentrate on subtle objects
	\item  Nirvichara (निर्विचार): go beyond subtle objects
	\item  Ananda (आनन्द) : concentrate on bliss
	\item  Asmita (अस्मिता) : concentrate on the pure I-sense
	\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{Practical Guidelines for Meditation}


	\begin{itemize}
	\item Practice on an empty stomach, in the early hours of the 
morning. Time permitting, practice in the evening as well.
	\item Find a clean, quiet area, away from door bells, telephones or other 
distractions, for meditation. Use the same location everyday. 
	\item In the Hatha Yoga tradition, meditation is usually practiced after 
performing asana (physical postures), relaxation and pranayama
(breathing techniques). As a result of these practices, the body and mind 
are better prepared for meditation.
	\item  Avoid meditation when the mind is agitated or emotionally disturbed
	\item Use any comfortable sitting posture for meditation. If sitting on the floor is 
uncomfortable, sit in a chair or rest the back against a wall.
	\item  During meditation, maintain a perfectly still body with the spine upright, 
shoulders relaxed and the hands resting comfortably on the knees or 
thighs.
	\item  The recommended duration for meditation is 20 to 30 minutes. The 
duration can be adjusted up or down depending upon the availability of 
time.
	\end{itemize}

\tiny{(Ref: Eight Limbs of Yoga - Subhash Mittal)}

\end{frame}